What is happening on Twitter? A framework for student research projects with tweets

### 2020-11-02 Rmd/reply-to-reviewers-nov2020.Rmd

---
output: 
  bookdown::pdf_document2:
    toc: false
    number_sections: false
---

November 2, 2020

Dear editors and reviewers:

We are writing to submit an updated manuscript that incorporates the suggested edits.

We include both the text of the comments and our replies.

## Editor's Comments to Author:

* unfortunately, I don't think JSE has formatting guidelines for packages. However, they should be internally consistent in
your paper (e.g., bold, quoted, without format, etc.): rtweet, tidytext, lubridate,...

> We now do this for all packages that we discuss in the text.

* API stands for application programming interface (not application product interface)

> Thank you for this correction. We've made the change.

* how was table 1 ordered? As is, the sorting is (seemingly?) arbitrary, and I think it would be easier to read if sorted. I’d
suggest one of two ways:
- sort by order of category
- sort by the order in which the skills are performed in a standard data analysis.

> Thank you. We now order the rows by category.

* page 10, line 12 “eg., “ should be “e.g.,”

> We've now made this change.

* page 10, line 32. You discovered evidence to “support his strategy” ... what is his strategy? Do you mean to “support his
hypothesis”? or maybe to “support his ideas” ?

> Thank you. We decided to use "support his ideas".

* page 10, line 34 “We share below a case study based on this approach.” I’d clarify to say “Below, we share a case study
on a different widely discussed topic which is analyzed using an approach similar to that from the Super Bowl tweets.”

> Thanks. We've made this change.

* page 12, line 32 ... still something is off as I read the word JSON. You write: “Below is an example of JSON for one
tweet.” Here are some possible alternatives:
- “Below is an example of a JSON entry for one tweet.”
- “Below is an example of a JSON file for one tweet.”
- “Below is an example of a tweet in JSON format.”

> Thank you. We've chosen to use the last of the three suggested wordings.

* “to wrangle the tweet JSON into” (instead change to: “to wrangle the JSON tweet into” or “to wrangle the tweet JSON
data into”) page 13, line 46

> Thanks. We've made this change by using the latter suggested wording.

* I think “document by term matrix” should be “document-term matrix”

> We agree. We've made the changes.

* page 10: suggest changing 'may not be "safe for work"' to "may be "not suitable for work (NSFW)" and add a similar
warning to the Figure 1 caption. Would an additional sentence noting that instructors could have students remove words
from a list of common expletives or inappropriate words?

> Thanks. We've fixed this wording.

* Would it make sense to have all of the supplementary files available on a new public GitHub repo? That would simplify
references and updates.

> Yes, all files are in a Github repo at https://github.com/fboehm/jse-2019. If an additional (new) repo is needed, we're happy to make one.

### 2020-11-02 Rmd/jse-special-issue-2020-november.Rmd
updated ms AND reply to comments. Updated pdf of ms

Readers may need to slightly amend the above line to conform to requirements of 
their operating system's software. Readers who use Mac OS may proceed as we did, 
while those with Windows operating systems may consider using the R package 
"taskscheduleR" to schedule API queries via the Windows task scheduler [@taskscheduleR].

@@

The next task is to wrangle the tweet JSON into a data structure suitable for LDA modeling. 
We used functions from the `rtweet` R package to parse tweet JSON into a data frame. 
We then divided tweet text into words with functions from the `tidytext` R package. We 
discarded commonly used "stop words" and emojis.

@@

```{r, may24, fig.cap = "Top terms for LDA model from May 24, 2020"}
knitr::include_graphics("../results/beta-2020-05-24.png")
```

```{r, may25, fig.cap = "Top terms for LDA model from May 25, 2020 (Memorial Day). Results contain expletives and may be 'not suitable for work (NSFW)'."}
knitr::include_graphics("../results/beta-2020-05-25.png")
```

>>>>

Readers may need to slightly amend the above line to conform to requirements of 
their operating system's software. Readers who use Mac OS may proceed as we did, 
while those with Windows operating systems may consider using the R package 
`taskscheduleR` to schedule API queries via the Windows task scheduler [@taskscheduleR].

@@

The next task is to wrangle the tweet JSON data into a structure suitable for LDA modeling. 
We used functions from the `rtweet` R package to parse tweet JSON into a data frame. 
We then divided tweet text into words with functions from the `tidytext` R package. We 
discarded commonly used "stop words" and emojis.

@@

```{r, may24, fig.cap = 'Top terms for LDA model from May 24, 2020. Results contain expletives and may be "not suitable for work (NSFW)".'}
knitr::include_graphics("../results/beta-2020-05-24.png")
```

```{r, may25, fig.cap = "Top terms for LDA model from May 25, 2020 (Memorial Day)."}
knitr::include_graphics("../results/beta-2020-05-25.png")
```

### 2020-11-02 Rmd/jse-special-issue-2020-november.tex
updated ms AND reply to comments. Updated pdf of ms

\usepackage{graphicx,grffile}

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
%\usepackage[utf8x]{inputenc}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

Some social media data, including tweets from Twitter, is
available through website application product interfaces (APIs).
By way of a streaming API, Twitter shares a sample of approximately
one percent of all
tweets during an API query time period (``Sampled stream'' 2019). Any Twitter
user can freely
access this one percent sample, whereas access to a larger selection is available to
researchers for a fee.

@@

\caption{\label{tab:circle-table}Classifying project skills}
\centering
\begin{tabular}[t]{|>{}l|>{}l|}
\hline
Skill & Category\\
\hline
Structure research project files as R package & Worth being familiar with\\
\hline
Communicate results in speaking and in writing & Enduring understanding\\
\hline
Formulate a research question & Enduring understanding\\
\hline
Develop data science strategies to address research question & Enduring understanding\\
\hline
Use Github to share code and documentation & Important to know and do\\
\hline
Use git for version control & Important to know and do\\
\hline
Use text analysis tools to analyze tweets & Enduring understanding\\
\hline
Use cluster computing as needed & Worth being familiar with\\
\hline
Use data visualization to clarify and inform quantitative analyses & Important to know and do\\
\hline
Translate analysis results into scientific conclusions & Enduring understanding\\
\hline
Incorporate supplementary data sources into analysis & Important to know and do\\
\hline
Acquire data from internet sources & Important to know and do\\
\hline
Describe assumptions and limitations of statistical analyses & Enduring understanding\\
\hline
\end{tabular}
\end{table}

@@

Our first student examined relationships over time between
stock market index prices and tweet sentiment. For each day in her 12-month study period,
she identified stock market-related tweets with a key word search. With the complete
texts of stock market-related tweets for each day, she calculated a daily sentiment score and plotted it over time.
Her sentiment score reflected presence of emotion-associated terms
(\emph{eg}., ``happy'', ``sad'', ``mad'', ``scared'')
in tweet texts. Days with more net positive emotion words in the collected tweets received a higher
(positive) daily sentiment score, while days with more net negative words received a negative daily
sentiment score.
For her final project, she presented plots over time of her daily sentiment scores and daily closing
prices of the Standard and Poor's 500 index. She also explored time series analysis methods to quantify
relationships between index prices and sentiment scores.

Our second student developed social media event detection methods with topic
models. He hypothesized that tweet content changes over time, and that we
might detect these changes by comparing inferred tweet topics from distinct
time periods. To validate his hypothesis, he examined tweet content before, during, and after
the National Football League's Super Bowl game in 2015. He reasoned that
because the Super Bowl is widely discussed on Twitter, we might detect
Super Bowl-related topics from tweets sent during the game, but that the football-related
topics would be short-lived in the continuous Twitter stream. We discovered
evidence to support his strategy, and we ultimately presented our findings
at international and local research meetings. We share below a case study based
on this approach.

@@

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{*/5}\NormalTok{ * * * * R -e }\StringTok{'rtweet::stream_tweets(timeout = (60 * 5), }
\StringTok{parse = FALSE, file_name = paste0("~/work/mentoring/mentoring-framework/data/",}
\StringTok{lubridate::now(), "-tweets"))'}
\end{Highlighting}
\end{Shaded}

Readers may need to slightly amend the above line to conform to requirements of
their operating system's software. Readers who use Mac OS may proceed as we did,
while those with Windows operating systems may consider using the R package
``taskscheduleR'' to schedule API queries via the Windows task scheduler (Wijffels and Belmans 2018).

@@

Below is an example of JSON for one tweet.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{\{}
  \StringTok{"created_at"}\NormalTok{: }\StringTok{"Thu Apr 06 15:24:15 +0000 2017"}\NormalTok{,}
  \StringTok{"id_str"}\NormalTok{: }\StringTok{"850006245121695744"}\NormalTok{,}
  \StringTok{"text"}\NormalTok{: }\StringTok{"1\textbackslash{}/ Today we\textbackslash{}u2019re sharing our vision for the future of the Twitter API platform!"}\NormalTok{,}
  \StringTok{"user"}\NormalTok{: }\KeywordTok{\{}
    \StringTok{"id"}\NormalTok{: }\ExtensionTok{2244994945}\NormalTok{,}
    \StringTok{"name"}\NormalTok{: }\StringTok{"Twitter Dev"}\NormalTok{,}
    \StringTok{"screen_name"}\NormalTok{: }\StringTok{"TwitterDev"}\NormalTok{,}
    \StringTok{"location"}\NormalTok{: }\StringTok{"Internet"}\NormalTok{,}
    \StringTok{"url"}\NormalTok{: }\StringTok{"https:\textbackslash{}/\textbackslash{}/dev.twitter.com\textbackslash{}/"}\NormalTok{,}
    \StringTok{"description"}\NormalTok{: }\StringTok{"Your official source for Twitter Platform news, updates & events. }
\StringTok{    Need technical help? Visit https:\textbackslash{}/\textbackslash{}/twittercommunity.com\textbackslash{}/ \textbackslash{}u2328\textbackslash{}ufe0f }
\StringTok{    #TapIntoTwitter"}
  \KeywordTok{\}}\NormalTok{,}
  \StringTok{"place"}\NormalTok{: }\KeywordTok{\{}   
  \KeywordTok{\}}\NormalTok{,}
  \StringTok{"entities"}\NormalTok{: }\KeywordTok{\{}
    \StringTok{"hashtags"}\NormalTok{:}\BuiltInTok{ [}      
\NormalTok{    ],}
    \StringTok{"urls"}\NormalTok{: [}
\NormalTok{      \{}
        \StringTok{"url"}\NormalTok{: }\StringTok{"https:\textbackslash{}/\textbackslash{}/t.co\textbackslash{}/XweGngmxlP"}\NormalTok{,}
        \StringTok{"unwound"}\NormalTok{: \{}
          \StringTok{"url"}\NormalTok{: }\StringTok{"https:\textbackslash{}/\textbackslash{}/cards.twitter.com\textbackslash{}/cards\textbackslash{}/18ce53wgo4h\textbackslash{}/3xo1c"}\NormalTok{,}
          \StringTok{"title"}\NormalTok{: }\StringTok{"Building the Future of the Twitter API Platform"}
\NormalTok{        \}}
\NormalTok{      \}}
\NormalTok{    ],}
    \StringTok{"user_mentions"}\NormalTok{: [     }
\NormalTok{    ]}
\NormalTok{  \}}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

The next task is to wrangle the tweet JSON into a data structure suitable for LDA modeling.
We used functions from the \texttt{rtweet} R package to parse tweet JSON into a data frame.
We then divided tweet text into words with functions from the \texttt{tidytext} R package. We
discarded commonly used ``stop words'' and emojis.

LDA model fitting requires that the corpus be organized as a
document by term matrix. In a document by term matrix, each row corresponds to a single document (a single
tweet), and each column is a single term (or word). Each cell contains a
count (the number of
occurrences of a term in the specified document). We created a document by
term matrix with the R function \texttt{cast\_dtm} from the \texttt{tidytext} package.

@@

We identified the top ten most probable terms for each of ten topics in our models
(Figures \ref{fig:may24}, \ref{fig:may25}, \ref{fig:may26}).
We plotted the within-topic word probabilities as bar graphs. We see that topic-specific
word probabilities seldom exceed 0.05. We also note that some words are heavily weighted in
multiple topics. This observation complicates semantic topic interpretation. We
also caution that the results display expletives (that appeared on Twitter) and may
not be ``safe for work''.

\begin{figure}
\includegraphics[width=29.17in]{../results/beta-2020-05-24} \caption{Top terms for LDA model from May 24, 2020}\label{fig:may24}
\end{figure}

\begin{figure}
\includegraphics[width=29.17in]{../results/beta-2020-05-25} \caption{Top terms for LDA model from May 25, 2020 (Memorial Day)}\label{fig:may25}
\end{figure}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-blei2017variational}{}%
Blei, D. M., Kucukelbir, A., and McAuliffe, J. D. (2017), ``Variational inference: A review for statisticians,'' \emph{Journal of the American Statistical Association}, Taylor \& Francis, 112, 859--877.

@@

\leavevmode\hypertarget{ref-pelled2018little}{}%
Pelled, A., Lukito, J., Boehm, F., Yang, J., and Shah, D. (2018), ```Little Marco,'`Lyin'Ted,'`Crooked Hillary,' and the `Biased' media: How Trump used Twitter to attack and organize,'' in \emph{Digital Discussions}, Routledge, pp. 176--196.

@@

\leavevmode\hypertarget{ref-taskscheduleR}{}%
Wijffels, J., and Belmans, O. (2018), \emph{taskscheduleR: Schedule R Scripts and Processes with the Windows Task Scheduler}.

>>>>

\usepackage{graphicx}

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
%\usepackage[utf8x]{inputenc}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

@@

Some social media data, including tweets from Twitter, is
available through website application programming interfaces (APIs).
By way of a streaming API, Twitter shares a sample of approximately
one percent of all
tweets during an API query time period (``Sampled stream'' 2019). Any Twitter
user can freely
access this one percent sample, whereas access to a larger selection is available to
researchers for a fee.

@@

\caption{\label{tab:circle-table}Classifying project skills}
\centering
\begin{tabular}[t]{|>{}l|>{}l|}
\hline
Skill & Category\\
\hline
Communicate results in speaking and in writing & Enduring understanding\\
\hline
Formulate a research question & Enduring understanding\\
\hline
Develop data science strategies to address research question & Enduring understanding\\
\hline
Use text analysis tools to analyze tweets & Enduring understanding\\
\hline
Translate analysis results into scientific conclusions & Enduring understanding\\
\hline
Describe assumptions and limitations of statistical analyses & Enduring understanding\\
\hline
Use Github to share code and documentation & Important to know and do\\
\hline
Use git for version control & Important to know and do\\
\hline
Use data visualization to clarify and inform quantitative analyses & Important to know and do\\
\hline
Incorporate supplementary data sources into analysis & Important to know and do\\
\hline
Acquire data from internet sources & Important to know and do\\
\hline
Structure research project files as R package & Worth being familiar with\\
\hline
Use cluster computing as needed & Worth being familiar with\\
\hline
\end{tabular}
\end{table}

@@

Our first student examined relationships over time between
stock market index prices and tweet sentiment. For each day in her 12-month study period,
she identified stock market-related tweets with a key word search. With the complete
texts of stock market-related tweets for each day, she calculated a daily sentiment score and plotted it over time.
Her sentiment score reflected presence of emotion-associated terms
(\emph{e.g}., ``happy'', ``sad'', ``mad'', ``scared'')
in tweet texts. Days with more net positive emotion words in the collected tweets received a higher
(positive) daily sentiment score, while days with more net negative words received a negative daily
sentiment score.
For her final project, she presented plots over time of her daily sentiment scores and daily closing
prices of the Standard and Poor's 500 index. She also explored time series analysis methods to quantify
relationships between index prices and sentiment scores.

Our second student developed social media event detection methods with topic
models. He hypothesized that tweet content changes over time, and that we
might detect these changes by comparing inferred tweet topics from distinct
time periods. To validate his hypothesis, he examined tweet content before, during, and after
the National Football League's Super Bowl game in 2015. He reasoned that
because the Super Bowl is widely discussed on Twitter, we might detect
Super Bowl-related topics from tweets sent during the game, but that the football-related
topics would be short-lived in the continuous Twitter stream. We discovered
evidence to support his ideas, and we ultimately presented our findings
at international and local research meetings. Below, we share a case study on a different, widely discussed topic which is analyzed using an approach similar to that from the Super Bowl tweets.

@@

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{*/5}\NormalTok{ * * * * R {-}e }\StringTok{\textquotesingle{}rtweet::stream\_tweets(timeout = (60 * 5), }
\StringTok{parse = FALSE, file\_name = paste0("\textasciitilde{}/work/mentoring/mentoring{-}framework/data/",}
\StringTok{lubridate::now(), "{-}tweets"))\textquotesingle{}}
\end{Highlighting}
\end{Shaded}

Readers may need to slightly amend the above line to conform to requirements of
their operating system's software. Readers who use Mac OS may proceed as we did,
while those with Windows operating systems may consider using the R package
\texttt{taskscheduleR} to schedule API queries via the Windows task scheduler (Wijffels and Belmans 2018).

@@

Below is an example of a tweet in JSON format.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{\{}
  \StringTok{"created\_at"}\NormalTok{: }\StringTok{"Thu Apr 06 15:24:15 +0000 2017"}\NormalTok{,}
  \StringTok{"id\_str"}\NormalTok{: }\StringTok{"850006245121695744"}\NormalTok{,}
  \StringTok{"text"}\NormalTok{: }\StringTok{"1\textbackslash{}/ Today we\textbackslash{}u2019re sharing our vision for the future of the Twitter API platform!"}\NormalTok{,}
  \StringTok{"user"}\NormalTok{: }\KeywordTok{\{}
    \StringTok{"id"}\NormalTok{: }\ExtensionTok{2244994945}\NormalTok{,}
    \StringTok{"name"}\NormalTok{: }\StringTok{"Twitter Dev"}\NormalTok{,}
    \StringTok{"screen\_name"}\NormalTok{: }\StringTok{"TwitterDev"}\NormalTok{,}
    \StringTok{"location"}\NormalTok{: }\StringTok{"Internet"}\NormalTok{,}
    \StringTok{"url"}\NormalTok{: }\StringTok{"https:\textbackslash{}/\textbackslash{}/dev.twitter.com\textbackslash{}/"}\NormalTok{,}
    \StringTok{"description"}\NormalTok{: }\StringTok{"Your official source for Twitter Platform news, updates \& events. }
\StringTok{    Need technical help? Visit https:\textbackslash{}/\textbackslash{}/twittercommunity.com\textbackslash{}/ \textbackslash{}u2328\textbackslash{}ufe0f }
\StringTok{    \#TapIntoTwitter"}
  \KeywordTok{\}}\NormalTok{,}
  \StringTok{"place"}\NormalTok{: }\KeywordTok{\{}   
  \KeywordTok{\}}\NormalTok{,}
  \StringTok{"entities"}\NormalTok{: }\KeywordTok{\{}
    \StringTok{"hashtags"}\NormalTok{:}\BuiltInTok{ [}      
\NormalTok{    ],}
    \StringTok{"urls"}\NormalTok{: [}
\NormalTok{      \{}
        \StringTok{"url"}\NormalTok{: }\StringTok{"https:\textbackslash{}/\textbackslash{}/t.co\textbackslash{}/XweGngmxlP"}\NormalTok{,}
        \StringTok{"unwound"}\NormalTok{: \{}
          \StringTok{"url"}\NormalTok{: }\StringTok{"https:\textbackslash{}/\textbackslash{}/cards.twitter.com\textbackslash{}/cards\textbackslash{}/18ce53wgo4h\textbackslash{}/3xo1c"}\NormalTok{,}
          \StringTok{"title"}\NormalTok{: }\StringTok{"Building the Future of the Twitter API Platform"}
\NormalTok{        \}}
\NormalTok{      \}}
\NormalTok{    ],}
    \StringTok{"user\_mentions"}\NormalTok{: [     }
\NormalTok{    ]}
\NormalTok{  \}}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

The next task is to wrangle the tweet JSON data into a structure suitable for LDA modeling.
We used functions from the \texttt{rtweet} R package to parse tweet JSON into a data frame.
We then divided tweet text into words with functions from the \texttt{tidytext} R package. We
discarded commonly used ``stop words'' and emojis.

LDA model fitting requires that the corpus be organized as a
document-term matrix. In a document-term matrix, each row corresponds to a single document (a single
tweet), and each column is a single term (or word). Each cell contains a
count (the number of
occurrences of a term in the specified document). We created a document-term matrix with the R function \texttt{cast\_dtm} from the \texttt{tidytext} package.

@@

We identified the top ten most probable terms for each of ten topics in our models
(Figures \ref{fig:may24}, \ref{fig:may25}, \ref{fig:may26}).
We plotted the within-topic word probabilities as bar graphs. We see that topic-specific
word probabilities seldom exceed 0.05. We also note that some words are heavily weighted in
multiple topics. This observation complicates semantic topic interpretation. We
also caution that the results display expletives (that appeared on Twitter) and may be ``not suitable for work (NSFW)''.

\begin{figure}
\includegraphics[width=29.17in]{../results/beta-2020-05-24} \caption{Top terms for LDA model from May 24, 2020. Results contain expletives and may be "not suitable for work (NSFW)".}\label{fig:may24}
\end{figure}

\begin{figure}
\includegraphics[width=29.17in]{../results/beta-2020-05-25} \caption{Top terms for LDA model from May 25, 2020 (Memorial Day).}\label{fig:may25}
\end{figure}

@@

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-blei2017variational}{}%
Blei, D. M., Kucukelbir, A., and McAuliffe, J. D. (2017), ``Variational inference: A review for statisticians,'' \emph{Journal of the American Statistical Association}, Taylor \& Francis, 112, 859--877.

@@

\leavevmode\hypertarget{ref-pelled2018little}{}%
Pelled, A., Lukito, J., Boehm, F., Yang, J., and Shah, D. (2018), ```Little Marco,'\,`Lyin'Ted,'\,`Crooked Hillary,' and the `Biased' media: How Trump used Twitter to attack and organize,'' in \emph{Digital Discussions}, Routledge, pp. 176--196.

@@

\leavevmode\hypertarget{ref-taskscheduleR}{}%
Wijffels, J., and Belmans, O. (2018), \emph{taskscheduleR: Schedule R Scripts and Processes with the Windows Task Scheduler}.
\end{cslreferences}
